\chapter{Intro} \label{intro}

\begin{list_type}  
\item Most real world graphs are sparse graph
\item Many real world applications can be converted to graph traversal
\item Many solution, Parralizatino, different structure, algorithms, harware implementation, etc \ldots 
\item Some of the current solution
\item why is it important to improve this type of problems
\item How can this benefit from improvement
\item how are we solving the problem
\item Why we choose our solution(hardware acceleration not really explored)
\item how the result was.
\item why use HLS(because an interesting solution, able to test multiple solution in a short implementation time.)
\item 
\end{list_type}

Most real world graph can be convert over to sparse matrix. Some examples are social network sites such as Facebook and Twitter, where users are directly connected each others. While other networks, such as fans following bloggers or celebertie, are more directed graphs. In real world, people are also connected to eacg other in form such as realationships and friendships. By looking at how data propagate through the network, or graph, we can simulate and solve an array of different problems. Some examples would be, how disease spreads through a population or a society, how a viral video or \it{meme} can spread through the Internett, Such a simulation can even be applied during viral marketing and censorship of information. $Data diffusion$ is the effect where data is propagated through such a network, from one node, spreading to a neighbour node via edges connecting between them. We can see how Data Diffusion is applicable in different social field and technical problems, much like how we mentioned earlier with spreading disease through a population, censorships of the Internett, viral marketing and social experiments like the small world experiments. One key aspect of Data diffusion, is the selection of seed nodes, the nodes that are activated or "infected" in the initiation state. Those nodes will start as seeds, and spread information throughout the network and can infect the entire. We can look at the seed selections importance in an example. If we look at vaccination during outbreak of the flue or similar infectious disease. If there are a finite amount of vaccines available, who should be vaccinated to prevent the outbreak? If each person is a node in an sparse network, were an infected individual is an activated node, the seed-selection would be to find the /it{k} individual that would have largest impact on the network as a whole. By preventing those individual to be infected, we can prevent the pandemic before it begins. Another examples would be to market a new product by giving away free samples or the product. The reciver will then potentially influence its peer and thus boosting sale. Such studies of such sparse network is important and usefull. There are different algorithms to traverse such graph, one commonly known algorithm for traversing graphs is known as $Breadth first search$. 


For information diffusion or data diffusion, there are two main cases that we can look at, independent cascade model and Linear Threshold Model(LTM). Independent cascade model, much like Breadth First search traverse a graph through the edges. Each infected node have a chance to activate their respected neighbour. The main difference between Breadth First Search and ICM is that ICM have either a local probability,m or a global probability where the node would be spared or untouched. Independent cascade model can be looked at as during flue season, each carrier of the flue have a chance to pass the flue to another person. The Linear thershold model, unlike ICM have no global or local activation chance. The prerequisition of activation, is the percentage of activated neighbour. Each node have either a local percentage, or a global percentage to activate. If the amount of neighbour reach the threshold, the current node would be activated. Linear Threshold model can be looked at as a new product being promoted, where each node is a person who will  potentially adopt the new product.Whether if that person would be susceptible to such marketing would be dependent on how many of it's friend(neighbour node) have purchased that product. If a certain number of its friends have bought it, a certain threshold is meet and it will also purchase that product. This is known as the Linear thereshold model, where the activation is desided by the amount of activated neighbours to that node. Both model is interesting in its own, for this thesis, we will mainly focus on Independent Cascade model.  



The seed selection algorithm is a NP hard problem, to select the seeds, we would have to run the algorithm for every node and their equivalent combination, for n nodes that would mean $n^2$ itterations. There are different optimization schemes that would reduce computation time, one that we would explore in this paper is optimization through hardware design. The main problem, is memory bandwidth, the so call memory wall(CITE NEEDED)

One field that lately have been getting some attention is the High Level Synthesis(HLS).  HLS takes high level code and synthesis it to machine codes and creaeting a optimal IP-core. The advantage with HLS is that unlike traditional hardware design, HLS converst high level languages such as C and C++ over to VHDL. This alows a much more flexible and productive implementation of the ip-core, you can test different solutions of the implementation by changing the C/C++ code and resynthesis to test different solution. The user would also not need to know how to write in traditional machine language. 

By having a dedicated machine designed to solve the seed selection problem, we can utilize it to have a quick way to simulate disease and viral marketing. graph traversal is also an important subject and applicable in many field. Simulation how disease spread, finding critical poerson to vaccinate, important link to censore to censore content. By creating dedicated hardware, we can reduce computation time and resource usage, compared to normal  (CITE YAMANS PAPER)

There are multiple benefits of designing a hardware solution to solve such a problem, such a algorithm have require multiple runs to solve such a task. Custom design of hardware to solve specific algorithm, combined with the fast prodution time with the HLS, a faster, morecustomizable design is possible.

High Level Synthesis is something develoeped by Xilinx, that allows creation of data design with C code. What High level synthesis can do,is convert your high level code(C/C++) to VHDL or VERILOG. (EXPLAIN WHAT VERILOG AND VHDL IS). 
HLS have matured much since the previous year, the idea of HLS have been worked on in the last year. Some of the pros with the HLS is that hardware design/FPGA design and implementation can be risen above the low level and give software programer the chance to implement specific designe and testing differend scheme and optimization would be easier to test with High Level Synthesis.

Custom cpu-fpga arcitecture[CITE YAMAN PAPER] have shown to imporve simlilar sparse mastrix vecotr multiplication. This leads us to want to explore the potential to a custom graph that solves the seed selection, which is a special case of BFS. 